Reproducibility in plant pathology: where do we stand and a way forward

### 2022-04-08 analysis/paper/paper.Rmd
Make brms version number reproducible by extracting from package in text

The statistical analysis was performed using R version 4.1.0 [@RCT2022] on an Apple MacBook Air (M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' (version 2.16.3) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.

>>>>

The statistical analysis was performed using R version 4.1.0 [@RCT2022] on an Apple MacBook Air (M1, 2020).
Bayesian mixed-effect models were fit using the contributed package 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] to evaluate the fixed effects of the publication (journal title), article class, molecular focus, five-year journal impact factor, journal open access policy on the reproducibility index and year to test for changes over time in the reproducibility index.
